---
title: "Listing Analysis"
author: "Mihir Bhaskar"
date: "26/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(message = FALSE)

# Clear workspace
rm(list = ls())

pacman::p_load(tidyverse, sp, leaflet, rgdal, maptools, tmap, stringr, ggthemes, knitr,
               ggmap)

# set up paths relative to User's Dropbox
if (Sys.info()[["user"]] == "mihirbhaskar") dbpath <- "/Users/mihirbhaskar/"
if (Sys.info()[["user"]] == "Sohaib Nasim") dbpath <- "C:/Users/Sohaib/"

base <- paste0(dbpath,"Dropbox/Mayur Vihar Project/")

# Import listing hh data
hh <- as.data.frame(read.csv(paste0(base,'full_master_hh_data.csv'))) 

# Import listing individual data
ind <- as.data.frame(read.csv(paste0(base,'full_master_ind_data.csv'))) 

# Import boundary shapefile, drawn using Google Maps and exported as .kml
# boundaries <- readOGR(paste0(base,"Listing Survey/Data/Raw/Blocks for listing.kml",
#                       require_geomType='wkbPolygon'))

# Dropping cases without HHID (basically cases that were found in the net distribution but didn't match)
hh <- hh[hh$hhid != "",]

# Creating / cleaning up categories for analysis


## Age
ind$age_group <- cut(ind$age, breaks = c(0,5,18,30,45,65,150), right = FALSE,
                     labels = c('Under 5','5-17 years', '18-29 years', '30-44 years', 
                                '45-64 years', '65 and above'))


## Length of stay
hh$length_of_stay <- factor(hh$length_of_stay, levels = 
                              c("","Keep coming and going","0 to 1 year","1 to 5 years",
                                "5 to 10 years","10 to 20 years","20 years or more"))

ind$length_of_stay <- factor(ind$length_of_stay, levels = 
                              c("","Keep coming and going","0 to 1 year","1 to 5 years",
                                "5 to 10 years","10 to 20 years","20 years or more"))


## Education

### Creating education category
ind$edu_group <- cut(ind$edu_level, c(-100,-87,4,9,11,12,15,18),
                     labels = c('Did not know or respond','Below primary/no formal education',
                                'Completed primary','10th pass','12th pass','Completed degree/diploma','Others'), right = TRUE) 

ind$edu_group[ind$edu_level == 16] <- 'Below primary/no formal education' # Anganwadi/nursery school reclassifying
ind$edu_group[ind$edu_level == 17] <- 'Below primary/no formal education' # Home schooled kids

# Creating easy table function for displaying using kable
tab <- function(x, y){
  
  y <- enquo(y)
  
  x %>% group_by(!!y) %>% summarise(n = n()) %>%
    
    mutate(percent = round((n/sum(n)), 3)) %>% arrange(desc(n))
  
}


# Exporting list of kids for nutrition interventions (6-16)
kids_6to16 <- ind %>% select(hhid, block, name, gender, dob, age, aadhaar_num, resp_name, phone_num) %>% 
  mutate(current_age = age + 1) %>% filter(current_age >= 6 & current_age <= 16) %>% group_by(hhid) %>% mutate(tot_kids_in_hh = n(), child_no = 1:n()) %>% ungroup() %>% select(-age) %>% rename(parent_name = resp_name)

kids_6to16 <- pivot_wider(kids_6to16, id_cols = c(hhid, block, parent_name, phone_num, tot_kids_in_hh),
                                   names_from = child_no,
                                   names_glue = "{.value}_{child_no}",
                                   values_from = c(name, gender, dob, aadhaar_num, current_age))

kids_6to16 <- select(kids_6to16, hhid, block, parent_name, phone_num, tot_kids_in_hh, contains("_1"), contains("_2"),
                              contains("_3"), contains("_4"), contains("_5"), contains("_6"), contains("_7"))

writexl::write_xlsx(kids_6to16, path = paste0(base,"kids_6to16.xlsx"))

# Exporting list of kids for nutrition interventions (0-5)
kids_0to5 <- ind %>% select(hhid, block, name, gender, dob, age, aadhaar_num, resp_name, phone_num) %>% 
  mutate(current_age = age + 1) %>% filter(current_age <= 5) %>% group_by(hhid) %>% mutate(tot_kids_in_hh = n(), child_no = 1:n()) %>% ungroup() %>% select(-age) %>% rename(parent_name = resp_name)

kids_0to5 <- pivot_wider(kids_0to5, id_cols = c(hhid, block, parent_name, phone_num, tot_kids_in_hh),
                                   names_from = child_no,
                                   names_glue = "{.value}_{child_no}",
                                   values_from = c(name, gender, dob, aadhaar_num, current_age))

kids_0to5 <- select(kids_0to5, hhid, block, parent_name, phone_num, tot_kids_in_hh, contains("_1"), contains("_2"),
                              contains("_3"), contains("_4"), contains("_5"), contains("_6"), contains("_7"))

writexl::write_xlsx(kids_0to5, path = paste0(base,"kids_0to5.xlsx"))

# Exporting list of mosquito net recipients for feedback

## Randomly sort HHs in the dataset
hh_copy <- hh
set.seed(928374)
rows <- sample(nrow(hh))
hh_copy <- hh_copy[rows,]

## Filter info for those who received nets
hh_copy <- hh_copy %>% filter(net_received == "Yes") %>% select(hhid, block, resp_name, phone_num, net_dist_date)

## Export to Excel
writexl::write_xlsx(hh_copy, path = paste0(base,"net_recipients_feedback_list.xlsx"))

rm(hh_copy)

```

## Demographics

```{r basic}

# Number of people per block
tab(hh, block) %>% kable(format.args = list(big.mark = ","), digits = 2, caption = "Number of households per block") 

# Creating map showing HH distribution of points

## Merging blockwise population onto the shapefiles

blocklevel <- as.data.frame(table(hh$block))

colnames(blocklevel)[1] <- "block"
colnames(boundaries@data)[1] <- "block"

boundaries@data <- merge(boundaries@data, blocklevel, by = 'block') 

## Creating leaflet plot with layers 

leaflet(hh[hh$location_accuracy <= 20,]) %>% addTiles %>% #addProviderTiles("Esri.WorldImagery") %>% 
  addPolygons(data = boundaries, color = 'black', weight = 1, highlightOptions = highlightOptions(color = "white", weight = 2, bringToFront = TRUE),
          popup = paste0('Block ',boundaries@data$block,': ',boundaries@data$Freq,' households')) %>%
  addCircles(~longitude, ~latitude, radius = 1, color = 'black')
  


# Household size distribution
hhsize_mean <- mean(hh$hh_size, na.rm = TRUE) %>% round(digits = 1)
hhsize_sd <- sd(hh$hh_size, na.rm = TRUE) %>% round(digits = 1)

ggplot(hh, aes(x = hh_size)) + 
  geom_bar(fill = 'tomato', color = 'firebrick4', alpha = 0.3) + 
  geom_vline(xintercept = hhsize_mean, size = 0.5) + 
  scale_x_discrete("Number of members in the household", breaks=1:10)+
  theme_tufte()+
  ggtitle("Distribution of household size", subtitle = paste("Mean =",hhsize_mean,"members | St. dev =",hhsize_sd))

# Gender distribution
tab(ind, gender) %>% filter(gender != "") %>% kable(caption = "Gender distribution")

# Individual age distribution
age_mean <- mean(ind$age, na.rm = TRUE) %>% round(digits = 1)
age_sd <- sd(ind$age, na.rm = TRUE) %>% round(digits = 1)

ind$under_18 <- as.factor(ind[,'age'] < 18)
levels(ind$under_18) <- c('Under 18 years','Above 18 years')

ggplot(ind, aes(x = age)) + 
  geom_histogram(aes(y = ..density.., fill = under_18), binwidth = 2) + 
  geom_density(size = 1, adjust = 5, color = 'firebrick4') + 
  ggtitle("Distribution of age", subtitle = paste("Mean =",age_mean,"years | St. dev =",age_sd)) 


ggplot(subset(ind, gender == 'Male' | gender == 'Female'), aes(x = age)) + 
  geom_histogram(aes(y = ..density..), binwidth = 2) + 
  geom_density(size = 1, adjust = 5, color = 'firebrick4') + 
  facet_wrap(~gender) +
  ggtitle('Age distribution by gender')

tapply(ind$age, ind$gender, mean)

tab(hh, religion) %>% kable(caption = 'Religious breakup of households')

ggplot(subset(ind, under_18 == 'Above 18 years' & edu_level != -89 & edu_level != -88)) + geom_bar(aes(x = edu_level)) +
  ggtitle('Over 18 years education distribution')

ggplot(subset(ind, under_18 == 'Above 18 years' & edu_level != -89 & edu_level != -88)) + geom_bar(aes(x = edu_level)) + ggtitle('Over 18 years education distribution') + facet_wrap(~gender)

tmp <- subset(ind, under_18 == 'Under 18 years' & age > 6 & edu_online_status != "")

tab(tmp, edu_online_status) %>% kable(title = 'Online schooling status, kids 6-18 years')

## Does having a sibling going to school improve your chances of going to school? Look at dynamics
## Between male sibling and female sibling

## Does 



```

## Access to services

```{r, echo = FALSE, message = FALSE, warning = FALSE}

tab(hh, length_of_stay) %>% kable(title = 'Length of stay of household')

# See if people are clustering in areas if they've been here longer

# leaflet(hh[hh$location_accuracy <= 20,]) %>% addTiles %>%
#   addCircles(~longitude, ~latitude, radius = 1, color = ~length_of_stay)

# Phone numbers; HHs sharing the same mobile number

tab(hh,phone_num) %>% select(n) %>% tab(n) %>% kable(caption = 'Mobile numbers by duplicate status')


# Verify with map or distance calculation that they are close to each other


# Creating tables of access to services

ind <- ind %>% mutate(has_ration_yesno = has_ration %in% c('Yes','Yes but does not want to provide details'),
               has_aadhaar_yesno = has_aadhaar %in% c('Yes','Yes but does not want to provide details'),
               has_voterid_yesno = has_voterid %in% c('Yes','Yes but does not want to provide details'),
               has_bankacc_yesno = has_bank_account %in% c('Yes','Yes but does not want to provide details'))

## Household-level - at least one person having access to these
hhlevelaccess <- ind %>% group_by(hhid) %>% summarise(hh_has_ration = max(has_ration_yesno),
                                     hh_has_aadhaar = max(has_aadhaar_yesno),
                                     hh_has_voterid = max(has_voterid_yesno),
                                     hh_has_bankacc = max(has_bankacc_yesno))

colMeans(hhlevelaccess[,2:5])


###### Export households that don't have ration for Vikram ####


hh <- merge(hh, hhlevelaccess, by = "hhid", all.x = TRUE)

forexport <- hh %>% filter(hh_has_ration == 0) %>% select(hhid, phone_num, length_of_stay, hh_size, contains('name'), contains('aadhaar_num'), contains('age'))

writexl::write_xlsx(forexport, path = "C:/Users/Mihir_Bhaskar/Desktop/hh_no_ration.xlsx")


# Correlations between these variables (figure out way to show correlation matrix highlighting cells as green etc.)
cor(hhlevelaccess[,2:5]) %>% round(2) 

## Individual-level
colMeans(ind %>% select(has_ration_yesno, has_voterid_yesno, has_aadhaar_yesno, has_bankacc_yesno))

cor(ind %>% select(has_ration_yesno, has_voterid_yesno, has_aadhaar_yesno, has_bankacc_yesno)) %>% round(2) 

# Cross-cuts:

# hhtest <- hhlevelaccess
# 
# for (i in 2:5){
#   hhtest[,i] <- factor(hhlevelaccess[,i])
# }



hh <- merge(x = hhlevelaccess, y = hh, by = 'hhid')

# Maps showing households
qmplot(data = hh[hh$location_accuracy < 20,], x = longitude, y = latitude, color = hh_has_ration)

qmplot(data = hh[hh$location_accuracy < 20,], x = longitude, y = latitude, color = hh_has_aadhaar)

qmplot(data = hh[hh$location_accuracy < 20,], x = longitude, y = latitude, color = hh_has_voterid)

qmplot(data = hh[hh$location_accuracy < 20,], x = longitude, y = latitude, color = hh_has_bankacc)



## Relationship between household length of stay and ration ownership
## In results file, have this as a stacked bar graph with # HHs under each category, filled as a 
## progress bar with access
ggplot(hh) + geom_bar(aes(x = length_of_stay, y = hh_has_ration),
                                 stat = 'summary', fun.y = 'mean') +
  ggtitle('Household length of stay vs ration card ownership')

## Relationship between HH length of stay and bank account ownership
ggplot(hh) + geom_bar(aes(x = length_of_stay, y = hh_has_bankacc),
                                 stat = 'summary', fun.y = 'mean') +
  ggtitle('Relationship between HH length of stay and bank account ownership')

## Relationship between Aadhaar ownership and age

ggplot(ind) + geom_bar(aes(x = age_group, y = has_aadhaar_yesno),
                                 stat = 'summary', fun.y = 'mean') +
  ggtitle('Relationship between Aadhaar ownership and age')

## Relationship between bank account ownership and age
ggplot(ind) + geom_bar(aes(x = age_group, y = has_bankacc_yesno),
                                 stat = 'summary', fun.y = 'mean') +
  ggtitle('Relationship between bank account ownership and age')


## Relationship between household size and access to services (are the people that are cut out single-person households? Or larger families?



## Relationship between access and gender
aggregate(ind %>% select(has_ration_yesno, has_voterid_yesno, has_aadhaar_yesno, has_bankacc_yesno),by=list(ind$gender), FUN = mean)



# See if there's a particular pocket of households that don't have access to Aadhaar or services (completely cut-out) - geography-wise

#ggplot(hh[hh$location_accuracy<20,]) + geom_point(aes(x = latitude.x, y = longitude.x, color = hh_has_aadhaar))

# Relationship between access and education level
aggregate(ind %>% select(has_ration_yesno, has_voterid_yesno, has_aadhaar_yesno, has_bankacc_yesno),by=list(ind$edu_group), FUN = mean)






```

- Household-level; ration card, with at least one member having a bank account
- % with aadhaar, % of hhs with ration, % of adults with bakn accounts, with voter IDs
(differences in bank account ownership between males and efmales, by age, by length of stay)

- Ration card and access to everything else by length of stay
- 
- Do these on a map with the dots to see an clear patterns

Bank account; check if it is correlated with age at all. Check the dynamics; if people co-located close to each other are more likely to have an account


